Study protocol

### 2021-08-19 Manuscript/S1.Protocol.Rmd
S1 first draft

---
title: "Study protocol"
date: `r lubridate::today()`
author:
  - first_name: "Angelo"
    last_name: "D'Ambrosio"
    url: http://github.com/bakaburg1/
    affiliation: Institute for Infection Prevention and Hospital Hygiene, Freiburg University Hospital
    affiliation_url: https://www.uniklinik-freiburg.de/iuk.html
    orcid_id: 0000-0002-2045-5155
output: distill::distill_article
---

@@

```{r query creation, echo = TRUE, eval = TRUE}

source('Setup.R') # Load the framework

@@

The query is passed to the `perform_search_session()` function, together with an unique identifier for the **search session** and **search query**. A session identifies a homogeneous group of complementary or alternative queries (e.g. sometimes it is easier to create two different simpler queries than a complex and long one that returns the same results).\
In our implementation we define as sessions the group of actions that includes the utilization of a search query and the subsequent cycle of manual review and relevancy prediction of its results.\

`perform_search_session()` will use common scientific research database APIs (at the moment Pubmed/Medline, Web of Science and IEEE) to look for records related to query, store them in a csv format and returns or update **journal** (a csv or excel file) with all the information about sessions, queries and search results. The records will be stored in folders with the following structure: Records/\*session_id\*/\*query_id\*. Some API requires API key to access the data. These keys can be stored in the secret.R file with the following structure:

```{r secrets}
options(ieee_api_key = 'bb58ndv4xbv535b5779u93ka')
options(ncbi_api_key = '5cd65c6d044db651af2bf8e9c78fc54fa409')
options(wos_api_key = 'C4O2SHqGc1rf3jmNxqI')
```

@@

If manually downloaded results are available, users can create the Record folders manually and put the data there (the file names need to contain the source name as written in the `sources` argument of `perform_search_session()`) and the function will acquire and parse them into a common format, even if split in multiple files due to download limits (e.g. Pubmed1.nbib, Pubmed2.nib, etc.). In addition of Pubmed, WOS and IEEE, this method permits to import also Embase and Scopus records, for which an API search was not yet implemented.\
Users can choose whether to perform an API search, parse already downloaded results, or both using the `actions` argument.

Note that for Pubmed, the API search may return slightly less records than a manual one due to a different query expansion algorithm (check Pubmed documentation) between the two services; therefore is advisable to perform also a manual search and put the resulting .nbib files in the Session/Query folder. `perform_search_session()` will acquire them seamlessly.

@@

```{r perform searches}
# This call will perform an API search on Pubmed, WOS and IEEE services and/or
# (based on the `actions` argument) parse already downloaded data (in our case, additional Pubmed results and Embase and Scopus results) manually added to the Session1/Query1 folder.
journal <- perform_search_session(query = query, year_query = year_filter,
																	session_name = 'Session1', query_name = 'Query1',
																	records_folder = 'Records',
																	journal = 'Session_journal.csv')

@@

```{r managing records}
# Create the first session
create_session(Annotation_data, session_name = 'Session1')
```

@@

Notice that the framework is "chaining" friendly and the precedent steps can be all performed in one call (which is the suggested procedure):

@@

# perform searches and parse files; save and return the journal
Records <- perform_search_session(query = query, year_query = year_filter,
											 session_name = 'Session1', query_name = 'Query1',
											 journal = 'Session_journal.csv') %>% 
	# return the record file paths
	extract_source_file_paths() %>%
	# read, join, reorder records and save them in the Sessions folder
	create_annotation_file(reorder_query = query) %>%  
	# Create a new session with the records
	create_session(session_name = 'Session1')
```

@@

Now the annotation file is ready for manual classification of relevant and non-relevant records. The annotation file has a column called `Rev_manual`, where records needs to be classified as "positve" (y) or negative (n) by the user. From our experience, around 250 manually classified records are sufficient if a minimum ~20% positivity rate is maintained (see the section about model parameter optimization)./
The function `check_classification_trends()` can help to visualize the trend of the positives/negatives as the number of classified records increases./

@@

- a results summary page which reports the number of records that need manual review (which includes uncertain and unreviewed positive records or records with certain predictions which are different from previous manual labels), the changes, and the final distribution of the labels; it also shows other information like the number of terms in the DTM, the path to the parent file from which the annotation file was created, the replication number (see later). The content of this summary is also saved as a csv file in the Results folder.
- a variable importance page which list the used terms in order of the fraction of BART trees in which they were used. If more than 1 model repetition is used, a more robust score is computed taking the ratio of the mean of the term tree fraction among models and its standard deviation.
- the arguments passed to the function if different from the default, useful for reproducibility.
- a classification performance summary (*this needs implementation*).

@@

Once the manual review of the generated annotation file is completed, the user can **rerun exactly the same function**. The reviewed annotation file will be automatically picked up and used for a new round of classification and review (CR). In case the number of records that require manual review is excessively high (e.g. > 250) the function need to be called setting the `stop_on_unreviewed` argument to `FALSE` to allow the classification to proceed even in the presence of unreviewed records (i.e. marked by "*") in the `Rev_prediction_new` column.

If there are no positive results (after manual review) in a CR round, the framework records the next round as a "replication". After four replication with no positive matches are done, the function will prevent another round and send a warning message. The user can change the replication limit; furthermore it's possible to have the function to stop if either a number (or a fraction of the total records) has been manually reviewed already, or if a certain number of positive matches have been found. These three parameter are passed to the `limits` argument which has the following structure and defaults:

@@

The result files in the Results folder are generated after the Classification phase but before the Review one, and therefore show preliminary results. The function `consolidate_results(session_name)` will update the results files to show the results after the manual review. The temporary result data is anyway stored in the respective annotations file.

@@

# The last annotation file and posterior sample matrix in the session are
# found; the most predictive terms (based on the importance score) are chosen
# and simple prediction trees are used to map the terms to a random subset of
# the posterior probabilities (extracted from the posterior sample matrix saved
# during the last CR step). The score threshold and the number of trees can be
# chosen by the user; less stringent values can greatly increase computation
# time;

@@

Once the new records are collected, `enrich_annotation_file('Session2')` can be used to perform the new CR cycles until no new positive matches are found. It may be possible that, during the first CR round, the number of records that require manual review is a large amount: we suggest to evaluate still not more than 250, keeping in mind to set the `stop_on_unreviewed` argument to `FALSE`.

@@

@@

As many complex machine learning models, the choosing of hyperparameters can greatly influence the framework performance. For a systematic review helper algorithm, we define the performance as the ability to find as many positive matches by manually labelling/reviewing as few records as possible.\
We added a number of simple tools to the framework to find a set of hyperparameters using by a "grid search" algorithm. We tested these tools on our dataset, manually labeling the first 1200 records (ordered by simple query match, as described when introducing the `create_annotation_file()` function)

>>>>

---
title: "Study protocol"
date: "`r lubridate::today()`"
output:
  github_document:
    html_preview: false
    toc: yes
---

@@

```{r query creation}

source('R/Setup.R') # Load the framework

@@

The query is passed to the `perform_search_session()` function, together with an unique identifier for the **search session** and **search query**. A session identifies a homogeneous group of complementary or alternative queries (e.g. sometimes it is easier to create two different simpler queries than a complex and long one that returns the same results).\
In our implementation we define as sessions the group of actions that includes the utilization of a search query and the subsequent iterations of manual review and automatic classification of its results.\

`perform_search_session()` will use common scientific research database APIs (at the moment Pubmed/Medline, Web of Science and IEEE) to look for records related to query, store them in a csv format and returns or update **journal** (a csv or excel file) with all the information about sessions, queries and search results. The records will be stored in folders with the following structure: `Records/session_id/query_id`. Some API requires API key to access the data. These keys can be stored in the `secrets.R` file with the following example code (the "baysren" prefix identify the package specific options):

```{r secrets}
options(baysren.ieee_api_key = 'your-ieee-api-key')
options(baysren.ncbi_api_key = 'your-ncbi-api-key')
options(baysren.wos_api_key = 'your-wos-api-key')
```

@@

If manually downloaded results are available, users can create the `Record` folder manually and put the data there (the file names need to contain the source name as written in the `sources` argument of `perform_search_session()`) and the function will acquire and parse them into a common format, even if split in multiple files due to download limits (e.g. `Pubmed1.nbib`, `Pubmed2.nib`, etc.). In addition of Pubmed, WOS and IEEE, this method permits to import also Embase and Scopus records, for which an API search was not yet implemented.\
Users can choose whether to perform an API search, parse already downloaded results, or both using the `actions` argument.

Note that for Pubmed, the API search may return slightly less records than a manual one due to a different query expansion algorithm (check Pubmed documentation) between the two services; therefore is advisable to perform also a manual search and put the resulting .nbib files in the `Session/Query` folder. `perform_search_session()` will acquire them seamlessly.

@@

```{r perform searches}
# This call will perform an API search on Pubmed, WOS and IEEE services and/or
# (based on the `actions` argument) parse already downloaded data (in our case, additional Pubmed results and Embase and Scopus results) manually added to the Session1/Query1 folder.
journal <- perform_search_session(
	query = query, year_query = year_filter,
	session_name = 'Session1', query_name = 'Query1',
	records_folder = 'Records',
	journal = 'Session_journal.csv')

@@

```{r create session}
# Create the first session
create_session(Annotation_data, session_name = 'Session1')
```

@@

Notice that the framework is "piping" friendly and the precedent steps can be all performed in one call (which is the suggested procedure):

@@

# perform searches and parse files; save and return the journal
Records <- perform_search_session(
	query = query, year_query = year_filter,
	session_name = 'Session1', query_name = 'Query1',
	journal = 'Session_journal.csv') %>% 
	# return the record file paths
	extract_source_file_paths() %>%
	# read, join, reorder records and save them in the Sessions folder
	create_annotation_file(reorder_query = query) %>%  
	# Create a new session with the records
	create_session(session_name = 'Session1')
```

@@

Now the annotation file is ready for manual classification of relevant and non-relevant records. The annotation file has a column called `Rev_manual`, where records needs to be classified as "positive" (y) or "negative" (n) by the user. From our experience, around 250 manually classified records are sufficient if a minimum ~20% positivity rate is maintained (see the section about model parameter optimization)./
The function `check_classification_trends()` can help to visualize the trend of the positives/negatives as the number of classified records increases./

@@

- a results summary page which reports the number of records that need manual review (which includes uncertain and unreviewed positive records or records with certain predictions which are different from previous manual labels), the changes, and the final distribution of the labels; it also shows other information like the number of terms in the DTM, the path to the parent file from which the annotation file was created, the replication number (see later). The content of this summary is also saved as a csv file in the Results folder.
- a variable importance page which list the used terms in order of the fraction of BART trees in which they were used. If more than 1 model repetition is used, a more robust score is computed taking the ratio of the mean of the term tree fraction among models and its standard deviation.
- the arguments passed to the function if different from the default, useful for reproducibility.
- a classification performance summary. The procedure may take some time and requires `cmdstan` installed on the machine. Therefore the `compute_performance` argument is set to FALSE by default.

@@

Once the manual review of the generated annotation file is completed, the user can **rerun exactly the same function**. The reviewed annotation file will be automatically picked up and used for a new iteration of classification and review (CR). In case the number of records that require manual review is excessively high (e.g. > 250) the function need to be called setting the `stop_on_unreviewed` argument to `FALSE` to allow the classification to proceed even in the presence of unreviewed records (i.e. marked by "*") in the `Rev_prediction_new` column.

If there are no positive results (after manual review) in a CR iteration, the framework records the next iteration as a "replication". After four replication with no positive matches are done, the function will prevent another iteration and send a warning message. The user can change the replication limit; furthermore it's possible to have the function to stop if either a number (or a fraction of the total records) has been manually reviewed already, or if a certain number of positive matches have been found. These three parameter are passed to the `limits` argument which has the following structure and defaults:

@@

The result files in the Results folder are generated after the Classification phase but before the Review one, and therefore show preliminary results with still unreviewed records. The function `consolidate_results(session_name)` will update the results files to show the results after the manual review. The temporary result data is anyway stored in the respective annotations file.

@@

# The last annotation file and posterior sample matrix in the session are
# found; the most predictive terms (based on the importance score) are chosen
# and simple prediction trees are used to map the terms to a random subset of
# the posterior probabilities (extracted from the posterior sample matrix saved
# during the last CR iteration). The score threshold and the number of trees can be
# chosen by the user; less stringent values can greatly increase computation
# time;

@@

Once the new records are collected, `enrich_annotation_file('Session2')` can be used to perform the new CR iteration until no new positive matches are found. It may be possible that, during the first CR iteration, the number of records that require manual review is a large amount: we suggest to evaluate still not more than 250, keeping in mind to set the `stop_on_unreviewed` argument to `FALSE`.

Finally a number of function is available (check `R/Reporting.R`) to summarise and format the results. For example, `summarise_by_source()` and `summarise_sources_by_session()`, respectively for one session or a group of sessions, summarise from which scientific database the records are collected from, while `get_source_distribution()` describe the distribution of the number of common sources per record.\
`summarise_annotations()` and `summarise_annotations_by_session()` describe the results of the CR iterations, again for one or many sessions, reporting the number of positive and negative matches, the number of terms (features) used by the machine learning model, and how the labels changes between iterations.
`format_performance()` and `format_var_imp()` format the output of the respective analyses.
`plot_predictive_densities()` plots how the mixture of posterior predictive distributions of records, divided in positive, negative and to-review records, change between iterations,

@@

A number of tools are available to evaluate the automatic classification performance.\
As said before, a result file is stored in the session folder for each CR iteration with a number of information on the classification status; remember to run `consolidate_results(session_name)` if you want these files to include also the manual review of the uncertain records.\
`compute_changes()` is a simpler function that take an annotation dataframe and computes the changes from the last annotation iteration.\
The main function for result analysis is `estimate_performance()`. The function uses a Bayesian model to estimate how the probability of a positive match drops as the lower boundary of the posterior predictive interval of each record decreases. This model allows to estimate the distribution of possibly missed positive records, which in turn permits to compute theoretical sensitivity and efficiency boundaries. Of course, the results are hypothetical since it is not possible to know the actual number of missed positive records.\
The function returns the Bayesian $R^2$ of the model (values below 85% would invalidate this analysis), the posterior sensitivity, the observed and theoretical number positives, the expected efficiency given the theoretical number of positives (that is 1 - the number of records reviewed above the number of records to review to find the predicted number of positives according to a negative hypergeometrical distribution). Also, the function plots the cumulative distribution of the observed and theoretical number of positive records.\
`extract_var_imp()` extract the most important terms used by the BART model and summarises their relevancy for the machine learning model and their statistical relevancy in a simple generalized linear model. Discrepancy between these two scores indicate a strongly non-linear effect of the terms.

@@

As many complex machine learning models, the choice of hyperparameters can greatly influence the framework performance. For a systematic review helper algorithm, we define the performance as the ability to find as many positive matches by manually labelling/reviewing as few records as possible:\

$$
Sensitivity \times Efficiency = \\
\frac{Pos.\ found}{Tot.\ pos.} \times \frac{Records\ reviewed}{Tot.\ records}
$$
We added a tools to the framework to find a set of hyperparameters using by a "grid search" algorithm. We tested these tools on our dataset, manually labeling the first 1200 records, ordered by simple query match.\
The first step is to create a folder where to store the file required for the search, for example *Grid Search*. Then a fully reviewed records file in the format generated by `create_annotation_file()` is necessary; this file can be put in the *Grid Search* but it is not mandatory. Once the folder and the file are ready run:

```{r grid search}
Grid_search <- perform_grid_evaluation(records, sessions_folder = 'Grid_Search',
																			 prev_classification = records,
																			 ## Model parameters, deg
																			 resample = c(FALSE, TRUE),
																			 n_init = c(50, 100, 250, 500),
																			 n_models = c(5, 10, 20, 40, 60),
																			 pos_mult = c(1, 10, 20),
																			 pred_quants = list(c(.1, .5, .9),
																			 									 c(.05, .5, .95),
																			 									 c(.01, .5, .99))
)
```

with `records` being the fully annotated data frame or a file path to it. `prev_classification` can be used to import a different classification file with prelabeled records.

The hyperparameters are the following:

* resample: whether to use bootstrapping to increase variability between the ensemble models;
* n_init: number of initial labelled records to train the machine learning model on;
* n_models: the number of models to fit and then average, in order to decrease the variance due to random sampling in the mcmc algorithm. It reduces the likelihood of extreme predictions;
* pos_mult: the oversampling rate of positive records. Useful to improve sensitivity;
* pred_quants: the distribution quantiles of each posterior prediction, used to define the uncertain records that require manual review.

Once the the grid search is performed, the function `analyse_grid_search()` can be used to analyze it's results. This function uses a partition tree analysis to identify hyperparameter sets (performance clusters) that are associated with a certain mean performance score. As said before, the default score is Sensitivity x Efficiency; alternatives are the Positive Rate (i.e., positive records found over total records), or Positive Rate x Sensitivity.\
The function produces a dataframe with the score and the cluster of each combination of parameters, the best hyperparameter set (i.e. the most efficient set among the most sensitive in the best cluster) and the best set for each cluster. Also, the function creates a plot that helps visualize the individual impact on performance of each hyperparameter.

Once chosen, the hyperparameters can be pass to `enrich_annotation_file()`.\
Mind that the grid search process may take many days even on powerful computers, so we suggest to stick to the default set of `enrich_annotation_file()`.
